---
title: "Homework 1"
auther: Yali Zhai
output: github_document
---

This is my solution to HW1

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements

```{r}
prob1_df = 
 tibble(
   samp = rnorm(10),
   samp_gt_0 = samp > 0,
   char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
   factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)

```

Take the mean of each variable in my data frame

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logic but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

## Problem 2

Download the package containing the penguins dataset


install.packages("palmerpenguins")

Load the penguins dataset:

```{r}
data("penguins", package = "palmerpenguins")
```

Description of the penguins dataset:

There are 5 numeric variables, which are bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g and year, and 3 factors, which are species, island and sex.

The mean of the bill_length_mm is `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)`.

The mean of the bill_depth_mm) is `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)`.

The mean of the flipper_length_mm is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

The mean of the body_mass_g is `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`.

The mean of the year is `r mean(pull(penguins, year), na.rm = TRUE)`.

The range of the bill_length_mm is `r range(pull(penguins, bill_length_mm), na.rm = TRUE)`.

The range of the bill_depth_mm is `r range(pull(penguins, bill_depth_mm), na.rm = TRUE)`.

The range of the flipper_length_mm is `r range(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

The range of the body_mass_g is `r range(pull(penguins, body_mass_g), na.rm = TRUE)`.

The range of the year is `r range(pull(penguins, year), na.rm = TRUE)`.

The size of the dataset is `r nrow(penguins)` * `r ncol(penguins)`.

The value of the species is `r levels(pull(penguins, species))`.

The value of the island is `r levels(pull(penguins, island))`.

The value of the sex is `r levels(pull(penguins, sex))`.

The scatter plot of flipper_length_mm (y) vs bill_length_mm (x)

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```


